Global case

### 2025-05-13 lipschitz 2025/Lipitschz.tex
update

@@

	\subsection{Improvement of the simplified model}

	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed.

@@

	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ are the follows: \begin{align*}
		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role binary for $\hat{x}'_i=\ReLU(x'_i)$.

@@

>>>>

However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which leads us to find another modeling approaches.

@@

	\subsection{Improvement of the simplified model}
	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed. (This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)

@@

	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows: \begin{align*}
		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$. The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.

@@

	A variant of the above model is to distinguish the binary variables $a'$s in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$, and relax all the latter ones.

	\section{Experiments}
